---
title: "R language"
output: html_notebook
---

#Sams Teach Yourself R
By Andy Nicholls, Richard Pugh, & Aimee Gott (first edition dec 2015)

##object types

4 modes (fonction mode()): 

  - numeric
  - character
  - boolean
  - complex

3 types (fonction class()): 

  - vector (c'est le type de base) - attributes length et names
  - matrix/array - attribut dim
  - list



#Advanced R

The book [Advanced R](https://adv-r.hadley.nz/) explains a lot of fundamental aspects of the R language.


The library **lobstr** allows to check the size of a variable 

```{r}
library(lobstr)
obj_size(1)
```

Main object types

```{r, echo=FALSE}
show_type <- function(element) {
  show(element)
  show(typeof(element))
  str(element)
}
```

```{r}
t1 <- c(1:5)
#attr(t1, "type") <- "vector of integers"
show_type(t1)
```

```{r}
t2 <- c(1.1, 1e2)
show_type(t2)
```

```{r}
t3 <- c("dog", "cat")
show_type(t3)
```

```{r}
t4 <- c(TRUE, FALSE)
show_type(t4)
```

```{r}
t5 <- list(1:2, 2:3)
show_type(t5)
```


```{r}
t6 <- data.frame(col1 = c(1:5), col2 = letters[1:5])
show_type(t6)
```